---
title: "MOAD statistics data"
author: "Seongmin Lee"
output: html_document
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(agricolae)
```

This page contains full statistical result of the paper <span style="font-weight:bold;">"MOAD: Modeling Observation-based Approximate Depedency"</span>, published on the Sourcs 19th IEEE international Working Conference on Source Code Analysis and Manipulation (SCAM 2019).

## 1. Comparison between model (RQ2, Page 7)

#### Summary of data:
```{r 1}
slice_size <- read.csv("data/slice_size.csv")
summary(slice_size)
```

### 1-1. On onehot data

```{r 1-1}
onehot_size_data <- slice_size[slice_size$scheme=='onehot_0',]
anova1 <- aov(size ~ infer, data = onehot_size_data)
summary(anova1)
print(HSD.test(anova1, 'infer', group=TRUE))
```

### 1-2. On 2hot data

```{r 1-2}
twohot_size_data <- slice_size[slice_size$scheme=='2hot_0',]
anova2 <- aov(size ~ infer, data = twohot_size_data)
summary(anova2)
print(HSD.test(anova2, 'infer', group=TRUE))
```

### 1-3. Overall

```{r 1-3}
a_both <- aov(size ~ infer * scheme, data = slice_size)
summary(a_both)
print(HSD.test(a_both, c('infer', 'scheme'), group=TRUE))
```


## 2. miss and excess (RQ3, Page 8)

#### Summary of data:
```{r 2}
miss_excess <- read.csv("data/miss_excess.csv")
summary(miss_excess)
```

### 2-1. miss between inference models

```{r 2-1}
anova_miss <- aov(miss ~ infer, data = miss_excess)
summary(anova_miss)
print(HSD.test(anova_miss, 'infer', group=TRUE))
```

#### 2-1-1. On line-level W-ORBS data

```{r 2-1-1}
me_W_line <- miss_excess[miss_excess$level == 'wline',]
anova <- aov(miss ~ infer * doe * proj, data = me_W_line)
summary(anova)
print(HSD.test(anova, c('infer', 'doe'), group=TRUE))
```

#### 2-1-2. On line-level T-ORBS data

```{r 2-1-2}
me_T_line <- miss_excess[miss_excess$level == 'tline',]
anova <- aov(miss ~ infer * doe * proj, data = me_T_line)
summary(anova)
print(HSD.test(anova, c('infer', 'doe'), group=TRUE))
```

#### 2-1-3. On statement-level T-ORBS data

```{r 2-1-3}
me_T_stmt <- miss_excess[miss_excess$level == 'tstmt',]
anova <- aov(miss ~ infer * doe * proj, data = me_T_stmt)
summary(anova)
print(HSD.test(anova, c('infer', 'doe'), group=TRUE))
```

### 2-2. excess between inference models

```{r 2-2}
anova_excess <- aov(excess ~ infer, data = miss_excess)
summary(anova_excess)
print(HSD.test(anova_excess, 'infer', group=TRUE))
```

#### 2-2-1. On line-level W-ORBS data

```{r 2-2-1}
me_W_line <- miss_excess[miss_excess$level == 'wline',]
anova <- aov(excess ~ infer * doe * proj, data = me_W_line)
summary(anova)
print(HSD.test(anova, c('infer', 'doe'), group=TRUE))
```

#### 2-2-2. On line-level T-ORBS data

```{r 2-2-2}
me_T_line <- miss_excess[miss_excess$level == 'tline',]
anova <- aov(excess ~ infer * doe * proj, data = me_T_line)
summary(anova)
print(HSD.test(anova, c('infer', 'doe'), group=TRUE))
```

#### 2-2-3. On statement-level T-ORBS data

```{r 2-2-3}
me_T_stmt <- miss_excess[miss_excess$level == 'tstmt',]
anova <- aov(excess ~ infer * doe * proj, data = me_T_stmt)
summary(anova)
print(HSD.test(anova, c('infer', 'doe'), group=TRUE))
```


## 3. Sampling effect (RQ4, Page 9)

#### Summary of data:
```{r 3}
sample_size <- read.csv("data/sample.csv")
summary(sample_size)
```

<!-- fig1_O <- fig1[fig1$infer == 'once_success',] -->
<!-- fig1_L <- fig1[fig1$infer == 'logistic',] -->
<!-- fig1_B <- fig1[fig1$infer == 'simple_bayes',] -->
<!-- a_fig1_O <- aov(size ~ scheme, data = fig1_O) -->
<!-- summary(a_fig1_O) -->
<!-- a_fig1_L <- aov(size ~ scheme, data = fig1_L) -->
<!-- summary(a_fig1_L) -->
<!-- a_fig1_B <- aov(size ~ scheme, data = fig1_B) -->
<!-- summary(a_fig1_B) -->
<!-- print(HSD.test(a_fig1_O, 'scheme', group=TRUE)) -->
<!-- print(HSD.test(a_fig1_L, 'scheme', group=TRUE)) -->
<!-- print(HSD.test(a_fig1_B, 'scheme', group=TRUE)) -->


### 3-1. On Once Success model data

```{r 3-1}
sample_size_O <- sample_size[sample_size$infer == 'once_success',]
anova <- aov(size ~ scheme, data = sample_size_O)
summary(anova)
print(HSD.test(anova, 'scheme', group=TRUE))
```

### 3-2. On Logistic model data

```{r 3-2}
sample_size_L <- sample_size[sample_size$infer == 'logistic',]
anova <- aov(size ~ scheme, data = sample_size_L)
summary(anova)
print(HSD.test(anova, 'scheme', group=TRUE))
```

### 3-3. On Bayesian model data

```{r 3-3}
sample_size_B <- sample_size[sample_size$infer == 'simple_bayes',]
anova <- aov(size ~ scheme, data = sample_size_B)
summary(anova)
print(HSD.test(anova, 'scheme', group=TRUE))
```

### 3-4. Overall

```{r 3-4}
anova <- aov(size ~ scheme * infer, data = sample_size)
summary(anova)
print(HSD.test(anova, c('infer', 'scheme'), group=TRUE))
```


<!-- You can also embed plots, for example: -->

<!-- ```{r pressure, echo=FALSE} -->
<!-- plot(pressure) -->
<!-- ``` -->

<!-- Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot. -->
